Innovation and elaboration on the avian tree of life - supplementary materials

### 2022-09-08 Manuscript/supplementaries.tex
Glossary draft

\section{Supplementary material 1: additional results}

@@

\section{Supplementary material 2: Passeriformes results}

@@

\section{Supplementary materials 3: detailed projection and rejection operations}
\label{supp_projection}

>>>>

\section{Supplementary material 1: glossary}

\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{llll}
  \hline
Term in this paper          & evolutionary biology definition & mathematics definition \\
  \hline
clade                       & a monophyletic group of species & a distance matrix associated with a subset of the \textbf{shapespace} \\ 
clade's major axis          & the \textbf{line of least resistance} specific to a clade & the first \textbf{eigenvector} of a \textbf{clade}'s \textbf{variance-covariance} matrix &  \\ 
eigenvector                 & one evolutionary \textbf{line of least resistance} for a clade & one of the vectors (direction) defining a \textbf{variance-covariance} matrix \\
elaboration                 & morphological score of a \textbf{species} or a \textbf{clade} in relation to a \textbf{line of least resistance} of reference & the \textbf{projection} of a \textbf{species} or a \textbf{clade} onto the first \textbf{eigenvector} of a \textbf{variance-covariance} matrix \\
family                      & a specific \textbf{clade} level (nested within \textbf{sub-orders}) & a distance matrix \\
higher taxa                 & a higher \textbf{clade} level & a distance matrix associated with a subset of the \textbf{shapespace} \\
innovation                  & morphological score of a \textbf{species} or a \textbf{clade} in relation to a \textbf{line of least resistance} of reference & the \textbf{rejection} of a \textbf{species} or a \textbf{clade} away from the first \textbf{eigenvector} of a \textbf{variance-covariance} matrix \\
lines of least resistance   & the major evolutionary ``direction'' of traits co-evolution & the first \textbf{eigenvector} or a \textbf{variance-covariance} matrix \\
macroevolution              & evolution above the species level & analyses using a portion of the entire shapespace \\
major axis                  & one of the ``directions'' of traits co-evolution & an \textbf{eigenvector} or a \textbf{variance-covariance} matrix; this can be represented as the longest orthogonal lines of an ellipse \\
megaevolution               & evolution above the \textbf{clade} level - here arbitrarily defined at the whole \textbf{phylogeny} level (i.e. all the birds) & analyses using the entire shapespace \\
order                       & a specific \textbf{clade} level (nested within \textbf{super-orders}) & a distance matrix associated with a subset of the \textbf{shapespace} \\
phylogenetic major axis     & the \textbf{line of least resistance} for the whole \textbf{phylogeny} & the first \textbf{eigenvector} of the whole \textbf{phylogeny}'s \textbf{variance-covariance} matrix \\
phylogeny                   & the relationships between all the \textbf{species} and their respective \textbf{clades} used in this analysis & a distance matrix associated with the whole \textbf{shapespace} \\
projection                  & the \textbf{elaboration} score of \textbf{species} or a \textbf{clade} & the position of a \textbf{species} or a \textbf{clade} onto an \textbf{eigenvector}\\
rejection                   & the \textbf{innovation} score of \textbf{species} or a \textbf{clade} & the distance of a \textbf{species} or a \textbf{clade} away from an \textbf{eigenvector} \\
residual                    & the variation in the \textbf{shapespace} not explained by the \textbf{phylogeny} or a \textbf{clade} & the error term in the pGLMM not explained by the random error terms (\textbf{phylogeny} and \textbf{clade}) \\
shapespace                  & all the observed morphological combination of the 8748 \textbf{species} of birds & a matrix where each columns are traits (or a transformation thereof, here they are principal components) and each rows are observations (here \textbf{species}). \\
species                     & the lowest evolutionary units in our analysis & rows in the \textbf{shapespace} matrix \\
sub-orders                  & a specific \textbf{clade} level (nested within \textbf{orders}) & a distance matrix associated with a subset of the \textbf{shapespace} \\
super-order                 & a specific \textbf{clade} level (the first nested level within the whole \textbf{phylogeny}) & a distance matrix associated with a subset of the \textbf{shapespace} \\
variance-covariance         & the traits co variation in the \textbf{shapespace} & the variation of the dimension within the \textbf{shapespace} taking into account the distance matrix between the observations (the \textbf{phylogeny} or the \textbf{clades}) \\

\end{tabular}
\caption{Glossary of some specific terms in this manuscript}
\label{tab_glossary}
\end{table}

\section{Supplementary material 2: additional results}

@@

\section{Supplementary material 3: Passeriformes results}

@@

\section{Supplementary materials 4: detailed projection and rejection operations}
\label{supp_projection}
